---
title: "ML course project"
author: "Cedric Bonjour"
date: "8/4/2020"
output: html_document
---


The goal of this project is to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways categorized from A to E. 



### Libraries 

```{r message=FALSE}
library(data.table)
library(caret)
```
### Loading pml data
```{r}
trn = fread("pml-training.csv")
tst = fread("pml-testing.csv")
```

### Data Cleaning & Exploratory Analysis

```{r}
info = c("rows" = nrow(trn), "col" = ncol(trn), "NA" = sum(is.na(trn)))
info = rbind(info, c(nrow(tst), ncol(tst),sum(is.na(tst)) ))
rownames(info) = c("train", "test")
info

```


Removing useless columns (first seven are metadata and many are full of NA thus unreliable)
And factoring the `classe` column

```{r}

b = (colSums(is.na(trn))<19000)

x =   trn[, ..b ]
x = x[, 8:ncol(x)]

y =   tst[, ..b ]
y = y[, 8:ncol(y)]

x$classe <- factor(x$classe)

dim(x)

```


### Preprocessing : center & scale numeric vars

```{r}
pp = preProcess(x[, 1:52])
px = predict(pp, x[, 1:52])
py = predict(pp, y[, 1:52])
px$classe = x$classe
py$classe = y$problem_id

```


### Cross validation set creation

```{r}
set.seed(7895)
b = createDataPartition(px$classe, p = 0.6, list=FALSE )
xtrn = px[b,]
xtst = px[-b,]

```



### Random forest 

```{r}

model_rf = train(classe ~ . , data=xtrn,  method="rf", trControl=trainControl(method="cv", number=3, verboseIter=FALSE), allowParallel=TRUE)

model_rf
```

## Cross validation of the model

```{r}

confusionMatrix(predict(model_rf, xtst), xtst$classe)
```
**Accuracy : 0.9913** is considered satisfying

### Prediction on test data

```{r}
predict(model_rf, py)
```

Quiz score : 100%



